---
title: "HW1"
author: "Shibei XU"
date: 2021-09-27
output: html_document
---

```{r loading_library,include = FALSE}
library(tidyverse)
```

# 1.Data input
First, we create a dataframe that comprised of: a random sample of size 10 from a standard Normal distribution;a logical vector indicating whether elements of the sample are greater than 0;a character vector of length 10
a factor vector of length 10, with 3 different factor “levels”

```{r df_create,echo=TRUE}
set.seed(123)

hw_df = tibble(
  vec_num = rnorm(10, sd = .5),
  vec_log = vec_num>0,
  vec```{r asnumeric,eval=FALSE, echo=TRUE}
as.numeric(hw_df,vec_log)
as.numeric(hw_df,vec_char)
as.numeric(hw_df,vec_factor)
```_char = character(10),
  vec_factor=factor(levels = c("a", "b" , "c"),10)
)
```

The mean of the variable `vec_num` is `mean(pull(hw_df, vec_num))`, of the `vec_log` is `mean(pull(hw_df, vec_log))`,`vec_char` is `mean(pull(hw_df, vec_char))`,`vec_factor` is `mean(pull(hw_df, vec_factor))`

```{r loaddataset,echo=FALSE}
install.packages("palmerpenguins")
```

Next we show a scatterplot of `y` vs `x`. 

```{r loaddata, echo=FALSE}
data("penguins", package = "palmerpenguins")
```

```{r}
summary(penguins)
nrow(penguins)
ncol(penguins)
```
```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm,color=species)) + geom_point()
```
```{r}
ggsave("scatter_plothomework.pdf", height = 4, width = 6)
```

